A Topic Model of Climate Change Literature

### 2019-07-10 main.tex
piers edits

		\noindent We live in an age of ``Big Literature'' 
		\cite{Nunez-Mir2016, Minx2017}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}. For example, in the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published in WoS (see Table \ref{tab}). This is almost as much as the 204,585 papers published during the first five assessment periods, a period of nearly 30 years. A total of about 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC. If we assume that WOS contains roughly about 41\% of the entire climate change literature (Khabasa), this yields a total number of new publications of around 850,000 for this assessment cycle. But the literature has also become more diverse. This is, for example, reflected in the expansion of vocabulary in this literature - from 2,000 unique words in AR1 to 94,746 words so far in AR6 - indicating that the field has incorporated new content. For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change. Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the WHO, is set to increase under rising global temperatures \cite{Rao2019}. Similar rapid emergences can be seen for [Intended] Nationally Determined Contributions ([I]NDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and REDD (The United Nations Collaborative Programme on Reducing Emissions from Deforestation and Forest Degradation in Developing Countries) in AR5, among others.

@@

		Big literature poses at least three challenges for scientific policy advice and its underlying science: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC fail to address the exploding literature base. For example, the ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l} and poses a rapidly growing risk of selection bias. More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature as often mandated is no longer possible for authors or author teams by traditional means. Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale (REFs). \emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods (REFs) - becomes increasingly important for aggregating and consolidating the rapidly emerging knowledge and enabling scientific assessments to do their job. Yet, traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications, whilst the field of evidence synthesis technology that tries to streamline human tasks through  at the different stages of the review process is still in its infancy (REFs). \emph{Finally}, overwhelming amounts of literature may be a major reasons why assessments of scientific assessments (REFs) do not offer robust quantifications, for example, between report citations and the underlying literature. This may substantially bias some of the findings.

		This study uses topic modelling \cite{Blei2010} to map out the vast body of evidence on climate change. Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus. The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (see Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change. Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.%To our knowledge, this is the first
		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a comprehensive understanding of the available climate science.

		\subsection{Mapping out the landscape of climate change literature}

		\begin{itemize}
			\item There is a broad and diverse range of topics
			\item The climate change literature is dominated by the Natural Sciences, but there is a range of interdisciplinary topics. Few topics are dominated by other discisplines.
			\item Topic growth within the landscape is dynamic. While most topics exist from the beginning, they show distinct patterhs of growth.
		\end{itemize}

		\subsection{Research representation in IPCC reports}

		\subsection{Discussion}

		\begin{itemize}
			\item Focus of our search - not a full representation - this may bias some of our results
			\item There is a much wider range of applications for this type of research
		\end{itemize}

		\subsection*{Proportionality in IPCC citations}

		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented. Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and Social and economic geography, political science, and other social sciences better represented than economics when taking into account the distribution of studies in the literature.

		This challenges what we think we know about the IPCC. The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports [1.5] times as high as in the literature at large.  On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with [2.5] and [3.5] times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively. % (Humanities are also underrepresented, but making up only 0.9\% of the wider literature, the proportionality is particularly sensitive).

@@

		%\subsection*{A Topography of Climate Change Research}

		Figure \ref{oecd_topic_map} shows the 400,000 documents on climate change in our dataset in a dimensionality reduction enabled representation of their topic structure, with topic labels placed near clusters of documents highly relevant to each topic. The map shows the high proportion of the natural sciences in climate change research, and the large proportion of the topic space dominated by natural science publications. These two features of the landscape account for the proportionally high share of natural science publications in IPCC citations.

		The thematic structure of the literature also maps well to the disciplinary structure, with clusters of social science topics, such as \textbf{policy}, \textbf{research}, \textbf{sector} and \textbf{growth} in the centre right of the graph, and natural sciences on the left. With reference to figure \ref{dis-entropy}, we can identify the topics which are more or less distributed across disciplines. \textbf{Coral}, for example, is almost exclusively discussed in the natural sciences, while papers on socio-economic issues are discussed in a variety of disciplines. Further, by using the topographical map, we can dig down further into the subject matter that is more or less proportionately represented, within and across disciplines.

@@

		%, and to further investigate the content of the documents that are more less proportionately represented in the IPCC.

		\begin{figure}
			\begin{center}
				\includegraphics[width=180mm]{plots_pub/topic_evolution_4.png}
				\caption{Evolution of the landscape of climate change literature}
				\label{evolution-map}
			\end{center}
		\end{figure}

		\subsection*{Supply and demand for solutions-oriented knowledge}

		Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map. Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports. It makes intuitive sense that these topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels}, are older, predominantly cited by WG I, and well cited by IPCC reports, as these are some of the core topics of the physical science of climate change.

		The topics in the lower right of the graph are the most pertinent to the question of whether the IPCC is well representing knowledge on climate change. These topics are newer and until now have been under-represented in IPCC reports. They are the topics that could be seen as potential gaps in the IPCC's coverage of the science. Because they are new areas of knowledge, they may be highly salient in a periodic assessment process. These topics are primarily in working group III (mitigation), with the exception of adsorption, CLC and hydrogen which are primarily of relevance to WG III but are miscategorised due to the low number of citations of relevant documents and citations of tangentially relevant documents by other working groups \footnote{For example, the word ``capacity" is relevant to the adsorption topic, so documents talking about adaptive capacity receive a low relevance score for that topic. Because only very few documents highly relevant to the adsorption topic (in that they talk about adsorption or adsorptive capacity) are cited by the IPCC, and many of the weakly relevant documents are cited by the IPCC, the sum of the topic scores of the weakly relevant WG II documents outweighs the sum of the topic scores of the strongly relevant WG III documents}.

		Although it is perhaps not surprising that these newer topics are less well represented than the older topics that make up the core of the physical science research on climate change, the difference between these new topics and other new topics that are better represented is intriguing. This difference is visible in figure \ref{evolution-map}, where the fastest growing topics in each period are labelled, and the documents are coloured according to the working group, if any, which cites them. In AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more. This is also evident in figure \ref{oecd_rep}c, where these topics display corresponding representation values. The IPCC, then, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II  than WG III topics.

		Within WG III topics, those that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b). The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research. \textbf{Waste}, \textbf{biochar}, \textbf{cement} and \textbf{coal}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research. This pattern is not visible in other working groups (see Figure \ref{socsci-wgs}), and complicates the perception of the under-representation of the social sciences.

		\subsection*{The IPCC as an informed decision-maker on topical representation}

		Deciding on the optimal proportion of each topic's literature to be cited by the IPCC is not a trivial task. A perfectly proportional representation of each topic is almost certainly not optimal, and as such, decisions about which topics to over-, or under- represent are best made by experts, not by a computer. Indeed, the IPCC itself is the best-placed institution to make these decisions. But in the age of ``Big Literature'' \cite{Nunez-Mir2016}, these decision should at best be underpinned by systematic knowledge of the landscape of the literature, and made in discussion with the wider research community, funders, policymakers and other stakeholders.

		The analysis in this study provide a useful input to this discussion. It could be argued that the under-represented technical literature on specific technological or sectoral solutions is not relevant to policymakers, and that working group III should give more weight to evidence about general policy instruments such as carbon taxes. Conversely, one could argue that establishing a technical understanding of specific climate solutions is as important a task as establishing a technical understanding of the physical science of climate change. The desire for more social science research in IPCC reports may imply, given the evidence here, that more social science research on climate change needs to be produced and funded, rather than that the IPCC should cite more of what already exists. Or, one could argue that, in light of the evidence that there is little social science research on solutions-relevant, under-represented topics, that the social sciences could do more to address technical or specific solutions such as negative emissions, green concrete, or waste and recycling.

		An understanding of the topography of the literature helps bring these arguments to the foreground, and allows them to be made in an informed way. Machine reading the literature in this way is not without its limitations though, and indeed many are apparent in this analysis. The corpus of potentially relevant literature is of course much wider than what is included in this study. The analysis excludes studies about climate change that do not match our query, studies relevant to tackling climate change that do not mention it specifically, studies written in languages other than English (unless the abstract has been translated), studies not indexed in the Web of Science, and reports published outside peer reviewed journals, not to mention Indigenous knowledge \cite{Ford2016b}. Despite this, unless the social science literature in the above categories is cited systematically less often  by the IPCC than the social science literature that was analysed in this study, then the main conclusions of this study hold. Topic models also carry limitations, and do not present the \textit{objective} truth about a corpus, given that they can be sensitive to modeller choices, such as the number of topics. However, the observations about the under-representation of solutions-relevant topics are robust across a broad range of topic numbers \ref{top-rep-ks}.

		Computational methods then, provide \textit{assistance} to humans in understanding a climate change literature that is produced by human individuals and institutions.  As in other areas of machine learning \cite{Barocas2016}, computational assessments of the literature run the risk of reproducing biases or gaps in the training data. However, just as with other applications of machine learning, machine-reading the science of climate change can provide information that helps us to understand gaps in what we have knowledge about, and potential biases, or options for emphasis, in how we represent that knowledge in the IPCC. In this way, we can more effectively meet the challenges posed by Big Literature to global environmental assessments.

@@

		\bibitem{Mulrow597}
		C~D Mulrow.
		\newblock {Systematic Reviews: Rationale for systematic reviews}.
		\newblock {\em BMJ}, 309(6954):597--599, 1994.

		\bibitem{Berrang-Ford2015}
		Lea Berrang-Ford, Tristan Pearce, and James~D. Ford.
		\newblock {Systematic review approaches for climate change adaptation
			research}.
		\newblock {\em Regional Environmental Change}, 15(5):755--769, 2015.

@@

		\bibitem{OMara-Eves2015}
		Alison O'Mara-Eves, James Thomas, John McNaught, Makoto Miwa, and Sophia
		Ananiadou.
		\newblock {Using text mining for study identification in systematic reviews: A
			systematic review of current approaches}.
		\newblock {\em Systematic Reviews}, 4(1):1--22, 2015.

		\bibitem{Westgate2018a}
		Martin~J. Westgate, Neal~R. Haddaway, Samantha~H. Cheng, Emma~J. McIntosh,
		Chris Marshall, and David~B. Lindenmayer.
		\newblock {Software support for environmental evidence synthesis}.
		\newblock {\em Nature Ecology and Evolution}, 2(4):588--590, 2018.

@@

		\bibitem{Barocas2016}
		Solon Barocas and Andrew~D Selbst.
		\newblock {Big Data's Disparate Impact}.
		\newblock {\em California Law Review}, 104:671--732, 2016.

>>>>

		\noindent We live in an age of ``Big Literature'' 
		\cite{Nunez-Mir2016, Minx2017l}, where the science of climate change is expanding exponentially \cite{Grieneisen2011, Haunschild2016}. In the five years since the publication of the last IPCC assessment report \cite{IPCC2014c}, 201,606 papers were published in the Web of Science (WoS) (see Table \ref{tab}). This is almost as much as the 204,585 papers published during the first five assessment periods, a period of nearly 30 years. A total of around 350,000 new publications can be expected for the current sixth assessment cycle of the IPCC, based on current growth patterns. Moreover, the literature has also become more diverse. This is reflected in the expansion of the literature's vocabulary - from 2,000 unique words in the first assessment period to 94,746 words so far in the sixth - indicating that the field has incorporated new content. For example, the zika virus, which was mentioned in 182 articles from 2014-2018, had never before been discussed in the titles or abstracts of articles relating to climate change. Yet it has emerged as a topic of high relevance: the incidence of the virus, the outbreak of which in Brazil in 2016 was declared a public health emergency by the WHO, is set to increase under rising global temperatures \cite{Rao2019}. Similar rapid emergence patterns can be seen for [Intended] Nationally Determined Contributions ([I]NDCs) and Sustainable Development Goals (SDGs) in AR6, and Biochar and REDD (The United Nations Collaborative Programme on Reducing Emissions from Deforestation and Forest Degradation in Developing Countries) in AR5, among others.

@@

		Big literature poses at least three challenges for scientific policy advice and science itself: \emph{First}, established procedures in scientific assessments like those conducted by the IPCC fail to address the exploding literature base. For example, the ratio of studies cited in IPCC reports to the number or relevant studies has declined from 60\% to 20\%  \cite{Minx2017l}, posing a rapidly growing risk of selection bias. More generally, the provision of comprehensive, objective, open and transparent assessments of the available scientific literature, as defined in the principles governing IPCC work \cite{IPCC2013}, is no longer possible for authors or author teams by traditional means. Machine reading and learning methods as well as other data science applications are required to enable an understanding of the field of climate change research at scale (REFs). \emph{Second}, evidence synthesis - the enterprise of reviewing the literature based on a formal and systematic set of methods \cite{Chalmers2002} - becomes increasingly important for aggregating and consolidating the rapidly emerging knowledge and enabling scientific assessments to do their job. Yet, traditional methods of evidence synthesis themselves are pushed to their limits by the large amount of scientific publications. Whilst the field of evidence synthesis technology that tries to streamline human tasks through machine learning at the different stages of the review process is still in its infancy \cite{Beller2018}. \emph{Finally}, overwhelming amounts of literature may be a major reasons why assessments of scientific assessments \cite{Bjurström2011, Hulme2010, Victor2015, Corbera2016} do not offer robust quantifications, for example, for claims about the relationship between report citations and the underlying literature. This may substantially affect findings.

		This study uses topic modelling \cite{Blei2010} to map out the vast body of evidence on climate change. Topic modelling is an unsupervised machine-learning technique, where patterns of word co-occurrences in documents are used to learn a set of topics which can be used to describe the corpus. The word topic derives from the Greek word for place (topos), and by \textit{situating} the documents in a reduced-form projection of their thematic content (see Figure \ref{oecd_topic_map}), we create a \textit{topographic map} of the literature on climate change. Such a systematic engagement with the thematic content of the climate science is missing from the literature so far.%To our knowledge, this is the first
		We apply this map in a second step to understand how the IPCC reports have represented the available climate change literature and re-evaluate claims of bias based on a more comprehensive understanding of the available climate science, and enrich the discussion of representation in the literature to include topics as well as disciplines.

		\subsection*{Mapping out the landscape of climate change literature}

		Figure \ref{oecd_topic_map} shows a \emph{thematic} or \emph{topopographic map} of the 400,000 publications on climate change in our dataset with a total number of 140 topics. The number of topics must be defined exogenously, but the results are robust to different specifications (see methods for examples and a thorough explanation of model selection). Using non-negative matrix factoriziation \cite{Lee1999}, the topics are machine-learned from the papers' abstracts (see methods for details).

@@

		The map shown covers a broad range of topics that occur in meaningful clusters. In general, topics related to climate science and impacts are in the West, while solution-oriented topics are in the East. More fine-grained research areas can also be distinguished. For example, publications related to urban infrastructure (buildings, energy, cement, waste) are located in the East (), physical climate impacts such as sea-level rise (), heat waves (), droughts () or crop yield (losses) () are in the South-West and energy systems are in North-East (). There are larger groups of documents at the fringes of the map that relate mainly to one or two specific topics such as biochar, corals, soil organic carbon, clouds and aerosols, diseases, membranes, absorption or adsorption or CO2 storage. Interestingly, scenarios feature centrally in the map, at the interface between different scientific communities. This corresponds to their integrative nature in IPCC reports (REF). This depiction of the thematic structure of the literature, and its ordering and categorising thereby could be useful for individual communities or for climate change assessments \footnote{We include the list of topic-document combinations in the supplementary materials}.

		The disciplinary composition of this research topography indicated by the different colours in Figure \ref{oecd_topic_map} highlights the dominance of natural sciences in climate change research. More than 60\% of the literature is published in natural science journals. Similarly, only in X out of 140 topics do publications from another field make up the majority of documents, in Y cases the contribution of publications in natural science journals make more than 50\%. We calculate disciplinary entropy of topics as a measure of their degree of interdisciplinarity (see Figure \ref{dis-entropy} and methods for details). While research on health, food, or policy comes from a range of disciplines, research on ice and oceans comes almost exclusively from the natural sciences).

		\begin{figure}
			\begin{center}
				\includegraphics[width=180mm]{plots_pub/topic_evolution_4.png}
				\caption{Evolution of the landscape of climate change literature. In each period, the 10 fastest growing topics are labelled. Where documents could be matched to IPCC citations, they are coloured by the working group citing them.}
				\label{evolution-map}
			\end{center}
		\end{figure}

		Finally, the topography shows the thematic evolution of the literature, with topics exhibiting distinct patterns of growth. Fast-growing topics in the last three assessment periods have included, among others, coral, risks, adaptation, hydrogen, buildings, CO2 removal, networks and biochar. Biochar is particularly remarkable in that the sizeable literature which emerged in AR5 was completely absent from the climate change literature beforehand. 
		The identification of new topics as they emerge, particularly as these are discovered without prior knowledge of the literature, can help researchers and assesment-makers to keep abreast of a quickly evolving field.

		\subsection*{Research representation in IPCC reports}
		We apply our topic map to understand the representation of science in IPCC assesssments and how it manages to respond to demands for more solution-oriented knowledge \cite{Kowarsch2017}. Several studies have identified, made, or repeated claims of a disciplinary bias of IPCC assessments towards the natural sciences, and within the social sciences towards economics \cite{Bjurström2011, Victor2015, Hulme2010, Corbera2016}. Where these claims were based on an analysis of IPCC citations \cite{Bjurström2011}, they fail to assess this claim against a reasonable, measurable benchmark. We argue here that the composition of the climate change literature as a whole provides such a benchmark, in view of the organisation's mandate to provide ``comprehensive, objective, open and transparent'' assessment of the available science \cite{IPCC2013}. Our comprehensive database allows us to study representation with such a benchmark, and over time rather than for single assessment cycles.

		Figure \ref{oecd_rep}.a shows that the social sciences were indeed under-represented in the third assessment report, but by the fifth assessment report were over-represented. Likewise, other social sciences than economics have become better represented since AR3  (see figure \ref{subfield}f) with social \& economic geography (4.3\% of the literature), political science (1.0\%), and sociology (0.8\%) showing improved representation in AR5 compared to AR3, and social and economic geography, political science, and other social sciences better represented than economics when taking into account the distribution of studies in the literature.

		This challenges what we think we know about the IPCC. The social sciences, by now, are actually the best represented field, with a share in the literature cited by IPCC reports [1.5] times as high as in the literature at large.  On the other hand the Agricultural Sciences and Engineering \& Technology have been consistently under-represented, with [2.5] and [3.5] times the share of studies in the wider literature than in the literature cited by the IPCC in AR5 respectively.

		The topography allows us to delve deeper into the subject matter that receives more or less attention in the IPCC. Figures \ref{oecd_rep}b and \ref{oecd_rep}c plot the representation of the topics shown in the map. Figure \ref{oecd_rep}c shows that topics more commonly cited by IPCC working group I are older and largely better represented in IPCC reports. These topics, for example \textbf{ozone}, \textbf{oceans}, \textbf{clouds}, \textbf{aerosols} and \textbf{sea levels}, are older, predominantly cited by WG I, and well cited by IPCC reports. They make up some of the core topics of the physical science of climate change.

		The topics in the lower right of the graph are the most pertinent to the question of whether the IPCC is well representing knowledge on climate change. These topics are newer and until now have been under-represented in IPCC reports. They are the topics that could be seen as potential gaps in the IPCC's coverage of the science. Because they are new areas of knowledge, they may be highly salient in a periodic assessment process. These topics are primarily in working group III, on mitigation (see methods section [] for a discussion of the categorisation of topics, including CLC, adsorption and hydrogen, which may more properly be of relevance to WGIII).

		The difference between these under-represented new topics and other new topics that are better represented is intriguing. This difference is visible in figure \ref{evolution-map}, where In AR5, the clusters of documents around the \textbf{adsorption}, \textbf{buildings}, and \textbf{biochar} topics contain few IPCC citations, whereas the clusters around \textbf{food}, \textbf{health}, \textbf{adaptation}, and \textbf{GHGs} contain more. As shown in figure \ref{oecd_rep}c, adsorption buildings and biochar are [4, 3.5 and 3.8] times more prevalent in the literature than in IPCC citations, while food is [0.3] times more prevalent in the literature and health and adaptation are [0.1] and [2,5] times more prevalent in IPCC citations respectively. The IPCC, then, has been better at integrating new knowledge from these topics, and in general better at integrating new knowledge from WG II  than WG III topics.

		Further, within WG III topics, those that are well represented contain a greater proportion of social science research (figure \ref{oecd_rep}b). The topics \textbf{countries}, \textbf{policy}, and \textbf{prices} are close to a proportional representation and are made up of around 30\% social science research. \textbf{Waste}, \textbf{biochar}, \textbf{cement} and \textbf{coal}, are more than 3 times more prevalent in the wider literature than in the literature cited by the IPCC, and are made up of around 5\% social science research. This pattern is not visible in other working groups (see Figure \ref{socsci-wgs}), and complicates the perception of the under-representation of the social sciences.

@@

		\subsection*{Machine-learning for climate change assessments}%, evidence synthesis and science of science} % needs to be reviewed
		Keeping track of developments in the scientific literature is becoming increasingly difficult in the age of big literature. This is becoming a central challenge for global environmental assessments such as those conducted by the IPCC \cite{Minx2017l, Kowarsch2017}, as well as for science of science research (\cite{Zeng2017}), the provision of thorough and comprehensive reviews in specific fields, and the efficient allocation of research funding where it is needed. Ultimately it is a challenge for sound, evidence-based scientific policy advice (\cite{White2019}). Systematic maps and evidence gap maps (\cite{James2016}, \cite{McKinnon2015}) provide crucial tools for tracing the literature, but current approaches are constrained by available resources to answering very specific questions, or are limited by a lack of suitable literature.  On the other hand, current scientometric and research weaving approaches (\cite{Nakagawa2019}) can capture a broader landscape of research, but are too unspecific with regard to the thematic content of literature.

		Elsewhere, we show how machine learning can accelerate the provision of traditional maps of evidence with thousands rather than hundreds of data points (\cite{Lamb2018d}). Here we extend this analysis to vast bodies of literature with hundreds of thousands of publications and show how ``topopgraphic maps'' provide an efficient visualisation of these.

		We acknowledge that the climate change topography presented here is not fully comprehensive. The WoS  covers a substantive, yet by no means exhaustive set of publications. Grey literature, some smaller journals and books, not to mention indigenous knowledge \cite{Ford2016b}, are not covered. Similarly, our query (see methods) requires that the keywords, title or abstract of a publication mentions climate change or a synonym or related term. Whilst this is a reasonable system boundary definition, and follows \cite{Grieneisen2011} exactly, we acknowledge the existence of directly relevant studies for climate change research - for example on energy technologies, energy policies or - that may not meet our criteria and remain outside the scope of our analysis. Yet our decisions are driven by data availability and requirements for a clean, climate-changed focused dataset. Given the large size of our sample (400,000+ publications), we argue that our topography provides a reasonable representation of the research landscape on climate change. Furthermore, unless IPCC citation patterns systematically differ in the not included parts of the literature, the main conclusions of this study are unaffected.

		In addition, our analysis is based on a topic model of publication abstracts. Though it is reasonable to assume that abstracts reflect the themes of the papers they describe, this depends on the quality of the abstracts, and thematic features of the underlying texts may not be adequately represented.  In the absence of comprehensive full-text access and remaining, non-trivial challenges in text extraction from PDFs, we argue that abstracts provide a reasonable unit of analysis.

		We apply our map of the climate change literature to understand the representativeness of IPCC citations and argue that answering related questions requires a clear benchmark. We show that applying this benchmark challenges and confirms some prominent findings around disciplinary representation in and solution-orientation of IPCC assessments.

		While proportional representation of all topics and all disciplines may not be desirable, the analysis presented here can help the IPCC to make quantitatively informed decisions about what to represent. The claim that the IPCC needs to incorporate more social science research may indeed be well-founded, but, in light of the fact shown here that the IPCC over-represents the social science literature that is published, this would imply increases in funding for climate change research in the social sciences. While some might argue that engineering or agricultural research on solutions related topics may be too technical and less relevant to IPCC assessments, in light of the size of the literature in these areas relative to that which is cited by the IPCC it would follow that more social science research needs to be carried out that deals with these topics and produces assessment-ready knowledge.

		We highlight that there are a variety of other immediate applications for such comprehensive topic maps and their rich, underlying data. Rapid, comprehensive maps could make a contribution to making climate change assessment processes in various places more efficient. For example, they could inform the scoping of scientific assessment reports to make sure that reports keep abreast of developments in the literature and remain policy relevant. What's more, they could help in the efficient identification of the best subject area experts across regions, sectors and genders (REFs) and directly increase the transparency with regard to the availability and selection of citations. Beyond the organisation of global environmental assessments, such maps can inform research funding decisions, and help individual researchers identi Future research can explore how further methods, and more comprehensive data, can help drive forward these applications.

		While the size and variety of the literature on climate change presents challenges to global environmental assessments, it represents a wealth of knowledge on vital climate solutions. By shedding light on new and under-reported subjects and by providing quantifications of what we think we know about how assessments and their relationship to the literature, computational mapping can help ensure that this knowledge is made use of efficiently.  Topographic maps  can become part of a toolbox which helps the IPCC continue to be able to fulfil its mandate of providing comprehensive, objective and transparent assessments of an expanding literature.

@@

		\bibitem{Beller2018}
		Elaine Beller, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl, Hans Lund,
		Mourad Ouzzani, Kristina Thayer, James Thomas, Tari Turner, Jun Xia, Karen
		Robinson, Paul Glasziou, and {On behalf of the founding members of the ICASR
			group}.
		\newblock {Making progress with the automation of systematic reviews:
			principles of the International Collaboration for the Automation of
			Systematic Reviews (ICASR)}.
		\newblock {\em Systematic Reviews}, 7(1):1--7, 2018.

		\bibitem{Lee1999}
		D~D Lee and H~S Seung.
		\newblock {Learning the parts of objects by non-negative matrix factorization.}
		\newblock {\em Nature}, 401(6755):788--791, 1999.

		\bibitem{Zeng2017}
		An~Zeng, Zhesi Shen, Jianlin Zhou, Jinshan Wu, Ying Fan, Yougui Wang, and
		H.~Eugene Stanley.
		\newblock {The science of science: From the perspective of complex systems}.
		\newblock {\em Physics Reports}, 714-715:1--73, 2017.

		\bibitem{White2019}
		Howard White.
		\newblock {The twenty-first century experimenting society: the four waves of
			the evidence revolution}.
		\newblock {\em Palgrave Communications}, 5(1):1--7, 2019.

@@

		\bibitem{Nakagawa2019}
		Shinichi Nakagawa, Gihan Samarasinghe, Neal~R. Haddaway, Martin~J. Westgate,
		Rose~E. O'Dea, Daniel~W.A. Noble, and Malgorzata Lagisz.
		\newblock {Research Weaving: Visualizing the Future of Research Synthesis}.
		\newblock {\em Trends in Ecology and Evolution}, 34(3):224--238, 2019.

		\bibitem{Lamb2018d}
		William~F. Lamb, Felix Creutzig, Max~W. Callaghan, and Jan~C. Minx.
		\newblock {Learning about urban climate solutions}.
		\newblock {\em Nature Climate Change}, 9(4):279--287, 2018.

@@

### 2019-07-10 methods.tex
draft 1
piers edits

	This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection. Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals.	Each document is assigned to an assessment period according to the timeline shown in table 1.

	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the web of science. Table \todo{}[x] shows the percentage of IPCC citations matched in each working group for each assessment report.

@@

	Data quality in earlier Web of Science results is poorer, and some documents have missing abstracts. In the quantification of the size of the literature and its vocabulary in table [], titles are substituted for abstracts where they are not available.  The words of the documents are lemmatized/stemmed, replacing different forms of the same word (i.e. word/words) with a single instance. Commonly occuring words, or ``stopwords'' are removed, as are all words shorter than 3 characters, and all words containing only punctuation or numbers.

@@

	For the calculation of the topic model, documents with missing abstracts are ignored, and the document term matrix is transformed into a document
	frequency-inverse document frequency (tf-idf) matrix, where scores are scaled according to the frequency of their occurence in the corpus. This gives more weight to terms which appear in few documents, and less weight to those which appear in many.

@@

	Topic models are calculated for 70, 80, 90, 100, 110, 120, 130 and 140 topics. The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information. The spreadsheet shows each set of topics in adjacent columns. Topics from each model are placed next to the topics with the largest number of each topic's 10 highest scoring words in common. This helps authors to find an appropriate level of granularity for the analysis.

@@

@@

@@

\linespread{1}
%\bibliography{Mendeley}

\begin{thebibliography}{1}

@@

	\bibitem{Lee1999}
	D~D Lee and H~S Seung.
	\newblock {Learning the parts of objects by non-negative matrix factorization.}
	\newblock {\em Nature}, 401(6755):788--91, 1999.

@@

>>>>

	This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on the Web of Science core collection. Though not exhaustive, the Web of Science gives a good coverage of the literature in major peer-reviewed journals. The Web of Science data gives us a disciplinary classification (based on the journal) and publication year, among other metadata, for each document.	Each document is assigned to an assessment period according to the timeline shown in table 1.

	We use the references scraped from IPCC assessment reports from \citep{Minx2017l}, and attempt to match these with the results from the Web of Science. We use doc2vec similarity scores \cite{Le2014} to identify the 500 most similar titles for each reference, and count the document as a match if the jaccard similarity score of the two word shingles of the reference title and the document title is greater than 0.5 \cite{Khabsa2014}. Table \ref{ipcc-matching} shows the percentage of IPCC citations matched in each working group for each assessment report. This is significantly lower in earlier periods, as data coverage and quality of citation databases is lower for earlier periods. Matching in WG III is also lower, suggesting a greater share of non-peer review literature, or literature not directly mentioning climate change, but related to it's mitigation (for example on energy policy).

		\begin{table}[htp]
			\begin{center}
		\input{tables/ipcc_matching.tex}
	\caption{IPCC matching}
	\label{ipcc-matching}
	\end{center}
\end{table}

@@

	Data quality in earlier Web of Science results is poorer, and some documents have missing abstracts. In the quantification of the size of the literature and its vocabulary in table \ref{tab}, titles are substituted for abstracts where they are not available.  The words of the documents are lemmatized, replacing different forms of the same word (i.e. word/words) with a single instance. Commonly occurring words, or ``stopwords'' are removed, as are all words shorter than 3 characters, and all words containing only punctuation or numbers.

@@

	For the calculation of the topic model, documents with missing abstracts are ignored, and the document term matrix is transformed into a document
	frequency-inverse document frequency (tf-idf) matrix, where scores are scaled according to the frequency of their occurrence in the corpus. This gives more weight to terms which appear in few documents, and less weight to those which appear in many.

@@

	Topic models are calculated for 70, 80, 90, 100, 110, 120, 130, 140 and 150 topics. The run with 150 topics was discarded as it contained a topic to which no terms or documents were assigned. The relative usefulness of each model was assessed subjectively by the authors, based on inspection of the online visualisation tool, and the spreadsheet \textbf{topic\_comparison.xlsx} accompanying the supporting information. The spreadsheet shows each set of topics in adjacent columns. Topics from each model are placed next to the topics with the largest number of each topic's 10 highest scoring words in common. This helps authors to find an appropriate level of granularity for the analysis.

@@

	\subsubsection*{Topic Map}
	The topic model gives us the location of each document in a 140 dimensional topic space, with each dimension corresponding to a that document's \textit{topic-ness} in a given topic. t-Distributed Stochastic Neighbour Embedding (t-SNE) is a dimensionality reduction technique which we use to represent each document's topic scores in 2 dimensions \cite{vandermaaten2008}.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots_pub/topic_rep_ks.pdf}
		\caption{Topic representation over different values of K (number of topics). Topics in the upper or lower 6.66th percentile of either dimension are labelled}
		\label{top-rep-ks}
	\end{center}
\end{figure}

@@

\linespread{1}

%\bibliography{Mendeley}

\begin{thebibliography}{10}

@@

	\bibitem{Le2014}
	Quoc~V. Le and Tomas Mikolov.
	\newblock {Distributed Representations of Sentences and Documents}.
	\newblock {\em ICML}, 32, 2014.

	\bibitem{Khabsa2014}
	Madian Khabsa and C~Lee Giles.
	\newblock {The number of scholarly documents on the public web}.
	\newblock {\em PLoS ONE}, 9(5), 2014.

	\bibitem{Lee1999}
	D~D Lee and H~S Seung.
	\newblock {Learning the parts of objects by non-negative matrix factorization.}
	\newblock {\em Nature}, 401(6755):788--791, 1999.

@@

	\bibitem{vandermaaten2008}
	Laurens van~der Maaten and Geoffrey Hinton.
	\newblock {Visualizing Data using t-SNE}.
	\newblock {\em Journal of Machine Learning Research}, 9:2579--2605, 2008.
